---
title: "Hospitals"
output: pdf_document
params:
  RA: RA
  Hospital_1: Hospital_1
  Hospital_2: Hospital_2

---

```{r libraries, include=FALSE, echo=FALSE}
library(readr)
library(tidyverse)
library(lubridate)
library(stringr)
library(knitr)
library(tibble)
```



```{r digits, messages =FALSE, include=FALSE, warnings = FALSE, echo=FALSE}
options(pillar.sigfig = 2)
```

```{r Hospital_1, messages =FALSE, include=FALSE, warnings = FALSE, echo=FALSE}
# read Hospital_1 Claims

Hospital_1 <- read_csv(params$Hospital_1, skip = 2)

# Transform Hospital_1

Hospital_1 <- Hospital_1 %>% mutate("First Name" = First,
                      "Last Name" = Last,
                      "Amt Submitted" = Fee,
                      "Service Date" = `S Date`)


# Detect skiped lines, Dr Name and RA Date
RAs <- read_lines(params$RA)
skip_h <- which(str_detect(RAs, "\"Group Number\"")) - 1
RA_h <- read_csv(params$RA, skip = skip_h, col_names = FALSE, n_max = 10)
Dr <- RA_h$X2[RA_h$X1 == "Payee"]
ra_date <- dmy(RA_h$X2[RA_h$X1 == "Payment Date"])
skip <- which(str_detect(RAs, "Accepted\\sClaims"))

# Read CSV
RAs <- read_csv(params$RA, skip = skip, guess_max = 3000)

# Clean RAs
RAs <- RAs[is.na(RAs$`First Name`) == FALSE,]
RAs <- RAs[!str_detect(RAs$NS, "NS"),]
RAs <- RAs[!is.na(RAs$NS),]
RAs$`Amt Paid`[is.na(RAs$`Amt Paid`)] <- 0

RAs <- RAs %>% mutate(
  `Amt Paid` = str_remove(RAs$`Amt Paid`, pattern = "\\$"),
  `Amt Submitted` = str_remove(RAs$`Amt Submitted`, pattern = "\\$"),
  `Amt Paid` = as.numeric(paste(`Amt Paid`)),
  `Amt Submitted` = as.numeric(paste(`Amt Submitted`)))


# Semi join
RAs <- semi_join(RAs, Hospital_1 , by = c("First Name","Last Name","Amt Submitted","Service Date"))

# Clean RAs
RAs <- RAs %>% select(`Last Name`, `Service Code`,
                      `Service Date`, NS, `Amt Submitted`,
                      `Amt Paid`) %>%
  mutate(`Service Date` = dmy(`Service Date`),
         Type = ifelse(RAs$`Service Code` == "G432A" |
                       RAs$`Service Code` =="G858A", "OHIP.VF",
                       "OHIP.Clinic"))

# Total
Total <- RAs %>% summarize("Hospital_1 Total" = sum(`Amt Paid`))
```


```{r Rejeciotns_Hospital_1, messages =FALSE, include=FALSE, warnings = FALSE, echo=FALSE}
Unpaid <- RAs[RAs$`Amt Paid` == 0,] %>% group_by(`Service Code`) %>%
  summarise(`Number of Claims` = n(),
            Unpaid = sum(`Amt Submitted`)) %>%
  arrange(desc(Unpaid))

RAs$Diff <- RAs$`Amt Submitted` - RAs$`Amt Paid`

`Partially Paid` <- RAs[RAs$Diff > 0 & RAs$`Amt Paid` != 0,] %>%
  group_by(`Service Code`) %>%
  summarise(`Number of Claims` = n(), Submitted = sum(`Amt Submitted`),
            Paid = sum(`Amt Paid`), Unpaid = sum(Diff)) %>%
  arrange(desc(Unpaid))

unpt <- sum(Unpaid$Unpaid)
punpt <- sum(`Partially Paid`$Unpaid)
```

# `r paste(Dr,"'S" ," remittance file paid by OHIP on ", ra_date, sep = "")`

# Hospital_1 Claims

`r paste("Hospital_1 Total = ",Total,"$")`
\newline


## Unpaid Claims
`r paste("Total unpaid =", round(unpt, digits = 2))`

```{r Unpaid_Hospital_1, echo=FALSE}
kable(Unpaid)
```

## Partially Paid Claims
`r paste("Total unpaid =", round(punpt, digits = 2))`
```{r PUnpaid_Hospital_1, echo=FALSE}
kable(`Partially Paid`)
```

## Payment per code

```{r Hospital_1 Total by code, warnings = FALSE, echo=FALSE}
# Summary
kable(RAs %>% group_by(`Service Code`) %>% 
        summarize("Number of services" = n(),
                  "Total" = sum(`Amt Paid`)) %>%
      arrange(desc(Total)))

```

## Payment per date
```{r Hospital_1 Total by date, warnings = FALSE, echo=FALSE}
kable(RAs %>% 
        group_by(`Service Date`) %>% 
        summarize("Weekday" = weekdays(unique(`Service Date`)),
                  "Number of services" = n(),
                  "Total" = sum(`Amt Paid`)))
#kable(arrange(RAs, `Service Date`))    
```

\newpage
# Hospital_2 Claims

```{r Hospital_2, messages =FALSE, include=FALSE, warnings = FALSE, echo=FALSE}
# read Hospital_2 Claims

Hospital_2 <- read_csv(params$Hospital_2, skip = 2)

# Transform Hospital_2

Hospital_2 <- Hospital_2 %>% mutate("First Name" = First,
                      "Last Name" = Last,
                      "Amt Submitted" = Fee,
                      "Service Date" = `S Date`)


# Detect skiped lines, Dr Name and RA Date
RAs <- read_lines(params$RA)
skip_h <- which(str_detect(RAs, "\"Group Number\"")) - 1
RA_h <- read_csv(params$RA, skip = skip_h, col_names = FALSE, n_max = 10)
Dr <- RA_h$X2[RA_h$X1 == "Payee"]
ra_date <- dmy(RA_h$X2[RA_h$X1 == "Payment Date"])
skip <- which(str_detect(RAs, "Accepted\\sClaims"))

# Read CSV
RAs <- read_csv(params$RA, skip = skip, guess_max = 3000)

# Clean RAs
RAs <- RAs[is.na(RAs$`First Name`) == FALSE,]
RAs <- RAs[!str_detect(RAs$NS, "NS"),]
RAs <- RAs[!is.na(RAs$NS),]
RAs$`Amt Paid`[is.na(RAs$`Amt Paid`)] <- 0
RAs <- RAs %>% mutate(
  `Amt Paid` = str_remove(RAs$`Amt Paid`, pattern = "\\$"),
  `Amt Submitted` = str_remove(RAs$`Amt Submitted`, pattern = "\\$"),
  `Amt Paid` = as.numeric(paste(`Amt Paid`)),
  `Amt Submitted` = as.numeric(paste(`Amt Submitted`)))


# Semi join
RAs <- semi_join(RAs, Hospital_2 , by = c("First Name","Last Name","Amt Submitted","Service Date"))

# Clean RAs
RAs <- RAs %>% select(`Last Name`, `Service Code`,
                      `Service Date`, NS, `Amt Submitted`,
                      `Amt Paid`) %>%
  mutate(`Service Date` = dmy(`Service Date`),
         Type = ifelse(RAs$`Service Code` == "G432A" |
                       RAs$`Service Code` =="G858A", "OHIP.VF",
                       "OHIP.Clinic"))

# Total
Total <- RAs %>% summarize("Hospital_2 Total" = sum(`Amt Paid`))
```

```{r Rejeciotns_Hospital_2, messages =FALSE, include=FALSE, warnings = FALSE, echo=FALSE}
Unpaid <- RAs[RAs$`Amt Paid` == 0,] %>% group_by(`Service Code`) %>%
  summarise(`Number of Claims` = n(),
            Unpaid = sum(`Amt Submitted`)) %>%
  arrange(desc(Unpaid))

RAs$Diff <- RAs$`Amt Submitted` - RAs$`Amt Paid`

`Partially Paid` <- RAs[RAs$Diff > 0 & RAs$`Amt Paid` != 0,] %>%
  group_by(`Service Code`) %>%
  summarise(`Number of Claims` = n(), Submitted = sum(`Amt Submitted`),
            Paid = sum(`Amt Paid`), Unpaid = sum(Diff)) %>%
  arrange(desc(Unpaid))

unpt <- sum(Unpaid$Unpaid)
punpt <- sum(`Partially Paid`$Unpaid)
```

`r paste("Hospital_2 Total = ",Total,"$")`
\newline

## Unpaid Claims
`r paste("Total unpaid =", round(unpt, digits = 2))`

```{r Unpaid_Hospital_2, echo=FALSE}
kable(Unpaid)
```

## Partially Paid Claims
`r paste("Total unpaid =", round(punpt, digits = 2))`
```{r PUnpaid_Hospital_2, echo=FALSE}
kable(`Partially Paid`)
```

## Payment per code
```{r Hospital_2 Total by code, warnings = FALSE, echo=FALSE}
# Summary
kable(RAs %>% group_by(`Service Code`) %>% 
        summarize("Number of services" = n(),
                  "Total" = sum(`Amt Paid`)) %>%
      arrange(desc(Total)))


```

## Payment per date
```{r Hospital_2 Total by date, warnings = FALSE, echo=FALSE}
kable(RAs %>% 
        group_by(`Service Date`) %>% 
        summarize("Weekday" = weekdays(unique(`Service Date`)),
                  "Number of services" = n(),
                  "Total" = sum(`Amt Paid`)))
#kable(arrange(RAs, `Service Date`))    
```


